---
title: "Getting started"
author: "Selcan Aydin"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_depth: 4
    toc_float: 
      collapsed: false
      smooth_scroll: false
    df_print: paged
    code_folding: show
    code_download: true
    theme: darkly
---

We will use `Rmarkdown` to analyze, plot and explain the data. There are a few essential packages that will make our results easier to reproduce and share. 


-  First one is the `renv` package which enables the recording of all R packages and versions used in an Rstudio project and sync. See more here: https://rstudio.github.io/renv/articles/renv.html

-  Second one is the `here` package which will let us use relative paths. When used together with Rstudio projects, `here()` function gets you to the Rstudio project main directory (i.e. where the .Rproj file is). We will use a `data` and `src` folders to keep our data and scripts organized. See more here: https://here.r-lib.org/


-  Finally, we will collaborate using github. Here is more detail on how to connect to github, cache your credentials and more on how to use github (<https://happygitwithr.com/>). 

## Initialize renv

Note that I set `eval =FALSE` since some of the code below needs to run just once and it requires you to answer prompts. 

```{r renv_activate, eval = FALSE}

# run to get renv() started
renv::init() # turn on renv. 
renv::settings$use.cache(TRUE) # use the local R libraries
renv::settings$snapshot.type("all") # record all R packages + dependencies

# run as needed
renv::hydrate()  
renv::snapshot() 

```

## Setup

Calling libraries that will be used in the project explicitly so that renv() can `hydrate`. 

```{r setup}

# libraries
library(here)
library(tidyverse)

```

## Use here()

The `here` package allows the use of paths relative to the Rstudio project working directory. 

```{r use_here}

here("data", "file_to_load.Rdata")

```


